---
title: "FE542Group1"
author: "Yuqi Liu"
date: "April 16, 2018"
output: word_document
---
## Package preparation
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(quantmod)
library(fUnitRoots)
library(forecast)
library(lubridate)
library(TSA)
library(fGarch)
```

## Generate data
```{r,warning=FALSE}
symbols <- c('CPIAUCNS','GDP','UNEMPLOY','INDPRO')
getSymbols(symbols, src='FRED')

# Visualization
par(mfrow=c(2,2))
plot(CPIAUCNS, main="Consumer Price Index", type="l")
plot(GDP, main="Gross Domestic Product", type="l")
plot(UNEMPLOY, main="Unemployment Level", type="l")
plot(INDPRO, main="Industrial Production Index", type="l")
```

## Determine the time interval/split the data into a trainning set and a test set
```{r,warning=FALSE}
date1 <- as.POSIXct("2009-02-27 02:00:00")
date2 <- as.POSIXct("2009-02-27 05:00:00")
Time_interval1 <- new_interval("1996-01-01", "2016-12-31")

#training set
CPI_tr <- CPIAUCNS[as.Date(rownames(as.data.frame(CPIAUCNS))) %within% Time_interval1,]
GDP_tr <- GDP[as.Date(rownames(as.data.frame(GDP))) %within% Time_interval1,]
UNEMPLOY_tr <- UNEMPLOY[as.Date(rownames(as.data.frame(UNEMPLOY))) %within% Time_interval1,]
INDPRO_tr <- INDPRO[as.Date(rownames(as.data.frame(INDPRO))) %within% Time_interval1,]

#calculate continues returns
Rt_CPI <- diff(log(CPI_tr))[-1]
Rt_GDP <- diff(log(GDP_tr))[-1]
Rt_UNEPLOY <- diff(log(UNEMPLOY_tr))[-1]
Rt_INDPRO <- diff(log(INDPRO_tr))[-1]
```

## Unit-Root Stationarity study
```{r,warning=FALSE}
#perform Augemented Dickey-Fuller test
adfTest(Rt_CPI,lag=ar(Rt_CPI)$order)
adfTest(Rt_GDP,lag=ar(Rt_GDP)$order) #unit-root exist
adfTest(Rt_UNEPLOY,lag=ar(Rt_UNEPLOY)$order)
adfTest(Rt_INDPRO,lag=ar(Rt_INDPRO)$order)
```

## CPI ARIMA Modeling
```{r}
tsdisplay(Rt_CPI)
# function for order determination
#AIC_CPI <- NULL
#for(p in 0 : 24)
#{
#  for(q in 0 : 24)
#  {
#    AIC_CPI <- c(AIC_CPI, arima(Rt_CPI, order = c(p, 0, q))$aic)
#  }
#}
```
```{r}
# show the result
#Order_Determine <- function(aic_vector, p_ori, q_ori)
#{
#  n <- which.min(aic_vector)
#  q <- (n %% (q_ori + 1))
#  if(q == 0)
#  {
#    p <- (n - n %% (q_ori + 1)) / (q_ori + 1) - 1
#    q <- q_ori
#  }else
#  {
#    p <- (n - n %% (q_ori + 1)) / (q_ori + 1)
#    q <- q - 1
#  }
#  print(paste("p", p, sep = "="))
#  print(paste("q", q, sep = "="))
#}
#Order_Determine(AIC_CPI,24,24)
# the result shows that ARMA(2,0,5) has the least AIC
```
```{r}
model.cpi <- arima(Rt_CPI, order = c(2, 0, 5))
summary(model.cpi)
#check model
tsdisplay(model.cpi$residuals)
# time period 24 shows slightly seasonality
# Adjusted model
tsdisplay(arima(Rt_CPI, order = c(2, 0, 5), seasonal = list(order = c(1,0,1), period = 9))$residuals)
model.cpi<-arima(Rt_CPI, order = c(2, 0, 5), seasonal = list(order = c(1,0,1), period = 24))
tsdisplay(model.cpi$residuals,lag=35)
#tsdiag(model.cpi)
Box.test(model.cpi$residuals,lag=11,type="Ljung")
Box.test(model.cpi$residuals,lag=28,type="Ljung")
```

## GDP ARIMA Modeling
```{r}
# since didn't pass ADF test, take differential of GDP and test again
dRt_GDP <- diff(Rt_GDP)[-1]
adfTest(dRt_GDP,lag=ar(dRt_GDP)$order)
tsdisplay(dRt_GDP)
#AIC_GDP <- NULL
#for(p in 0 : 24)
#{
#  for(q in 0 : 24)
#  {
#    AIC_GDP <- c(AIC_GDP, arima(dRt_GDP, order = c(p, 0, q))$aic)
#  }
#}
#Order_Determine(AIC_GDP,24,24)
# ARMA(2,1)
```
```{r}
model.gdp <- arima(Rt_GDP, order = c(2, 1, 1))
summary(model.gdp)
tsdisplay(model.gdp$residuals,lag=20)
tsdiag(model.gdp) #model ok
```

## Unemployment Level ARIMA Modeling
```{r}
tsdisplay(Rt_UNEPLOY)
#AIC_Une <- NULL
#for(p in 0 : 24)
#{
#  for(q in 0 : 11)
#  {
#    AIC_Une <- c(AIC_Une, arima(Rt_UNEPLOY,method = "ML", order = c(p, 0, q))$aic)
#  }
#}
#Order_Determine(AIC_Une,24,11)
```
```{r}
arima(Rt_UNEPLOY, order = c(6, 0, 5))$aic
arima(Rt_UNEPLOY, order = c(9, 0, 9))$aic
model.une <- arima(Rt_UNEPLOY, order = c(6, 0, 5))
summary(model.une)
tsdisplay(model.une$residuals)
tsdiag(model.une) #model ok
```

## Industrial Production ARIMA Modeling
```{r}
tsdisplay(Rt_INDPRO)
#AIC_INDPRO <- NULL
#for(p in 0 : 7)
#{
#  for(q in 0 : 6)
#  {
#    AIC_INDPRO <- c(AIC_INDPRO, arima(Rt_INDPRO, order = c(p, 0, q))$aic)
#  }
#}
#Order_Determine(AIC_INDPRO,7,6)
# The result shows that ARiMA(1,0,3) is the best
```
```{r}
arima(Rt_INDPRO, order = c(1, 0, 3))$aic
model.ip <- arima(Rt_INDPRO, order = c(1, 0, 3))
summary(model.ip)
tsdisplay(model.ip$residuals)
# time period 24 shows slightly seasonality
# Adjusted model
model.ip <-arima(Rt_INDPRO, order = c(1, 0, 3), seasonal = list(order = c(1,0,0), period = 24))
tsdisplay(model.ip$residuals)
tsdiag(model.ip)
```

## Prediction using ARIMA/Seasonal Models
```{r}
model.cpi<-arima(Rt_CPI, order = c(2, 0, 5), seasonal = list(order = c(1,0,1), period = 24))
model.gdp <- arima(Rt_GDP, order = c(2, 1, 1))
model.une <- arima(Rt_UNEPLOY, order = c(6, 0, 5))
model.ip <-arima(Rt_INDPRO, order = c(1, 0, 3), seasonal = list(order = c(1,0,0), period = 24))

pred.cpi<-predict(model.cpi,16)
pred.gdp<-predict(model.gdp,5)
pred.une<-predict(model.une,16)
pred.ip<-predict(model.ip,15)

rt_cpi <- diff(log(CPIAUCNS))[-1]
rt_gdp <- diff(log(GDP))[-1]
rt_unemploy <- diff(log(UNEMPLOY))[-1]
rt_indpro <- diff(log(INDPRO))[-1]
```
```{r}
# Visualization
plotr<-function(tik,data,pr,num,name,y){
  plot(tail(as.Date(rownames(as.data.frame(tik))),31),data[(length(data)-30):length(data)],type="l",ylim=y,main=name)
  points(tail(as.Date(rownames(as.data.frame(tik))),num),pr$pred,col="darkred")
  lines(tail(as.Date(rownames(as.data.frame(tik))),num),pr$pred,col="red")
  lines(tail(as.Date(rownames(as.data.frame(tik))),num),pr$pred+1.96*pr$se,col="royalblue")
  lines(tail(as.Date(rownames(as.data.frame(tik))),num),pr$pred-1.96*pr$se,col="royalblue")
}
par(mfrow=c(2,2))
plotr(CPIAUCNS,rt_cpi,pred.cpi,16,"CPI",c(-.0069,.0105))
plotr(GDP,rt_gdp,pred.gdp,5,"GDP",c(-.005,.023))
plotr(UNEMPLOY,rt_unemploy,pred.une,16,"Unemployment Level",c(-.065,.058))
plotr(INDPRO,rt_indpro,pred.ip,15,"Industrial Production",c(-.012,.015))
```

## Test ARCH effect
```{r}
# CPI 
Box.test((Rt_CPI-mean(Rt_CPI))^2, lag=12, type='Ljung')
#GDP
Box.test((Rt_GDP-mean(Rt_GDP))^2, lag=12, type='Ljung')
Box.test((dRt_GDP-mean(dRt_GDP))^2, lag=12, type='Ljung')
#Unemployment Rate
Box.test((Rt_UNEPLOY-mean(Rt_UNEPLOY))^2, lag=12, type='Ljung')
#Industrial Production
Box.test((Rt_INDPRO-mean(Rt_INDPRO))^2, lag=12, type='Ljung')
```
```{r}
# Further test
Box.test((arima(Rt_CPI, order = c(2, 0, 5))$res)^2, lag = 30, type = "Ljung")
Box.test((arima(Rt_GDP, order = c(2, 1, 1))$res)^2, lag = 30, type = "Ljung")
Box.test((arima(dRt_GDP, order = c(2, 0, 1))$res)^2, lag = 30, type = "Ljung")
Box.test((arima(Rt_UNEPLOY, order = c(6, 0, 5))$res)^2, lag = 30, type = "Ljung")
Box.test((arima(Rt_INDPRO, order = c(1, 0, 3))$res)^2, lag = 30, type = "Ljung")
```

## ARIMAX Modeling
```{r}
#  CPI
summary(arima(Rt_CPI, order = c(2, 0, 5), seasonal = list(order = c(1,0,1), period = 24), xreg=Rt_UNEPLOY))
summary(arima(Rt_CPI, order = c(2, 0, 5), seasonal = list(order = c(1,0,1), period = 24), xreg=Rt_INDPRO))
summary(arima(Rt_CPI, order = c(2, 0, 5), seasonal = list(order = c(1,0,1), period = 24), xreg=CPI_tr[-length(CPI_tr)]))
summary(arima(Rt_CPI, order = c(2, 0, 5), seasonal = list(order = c(1,0,1), period = 24), xreg=UNEMPLOY_tr[-length(UNEMPLOY_tr)]))
summary(arima(Rt_CPI, order = c(2, 0, 5), seasonal = list(order = c(1,0,1), period = 24), xreg=INDPRO_tr[-length(INDPRO_tr)]))
# Original model aic = -2227.92
```
```{r}
#GDP
#adjusted explanatory variables to quarterly
CPI_tr_quar <- NULL
for(i in 1 : length(CPI_tr))
{
  if(i %% 3 == 1)
  {
    CPI_tr_quar <- rbind(CPI_tr_quar, CPI_tr[i])
  }
}
Rt_CPI_quar <- diff(log(CPI_tr_quar))[-1]

UNEMPLOY_tr_quar <- NULL
for(i in 1 : length(UNEMPLOY_tr))
{
  if(i %% 3 == 1)
  {
    UNEMPLOY_tr_quar <- rbind(UNEMPLOY_tr_quar, UNEMPLOY_tr[i])
  }
}
Rt_UNEPLOY_quar <- diff(log(UNEMPLOY_tr_quar))[-1]

INDPRO_tr_quar <- NULL
for(i in 1 : length(INDPRO_tr))
{
  if(i %% 3 == 1)
  {
    INDPRO_tr_quar <- rbind(INDPRO_tr_quar, INDPRO_tr[i])
  }
}
Rt_INDPRO_quar <- diff(log(INDPRO_tr_quar))[-1]
```
```{r}
summary(arima(Rt_GDP, order = c(2, 1, 1), xreg = Rt_CPI_quar))
summary(arima(Rt_GDP, order = c(2, 1, 1), xreg = Rt_UNEPLOY_quar))
summary(arima(Rt_GDP, order = c(2, 1, 1), xreg = Rt_INDPRO_quar))
## GDP vs. dGDP
arima(Rt_GDP, order = c(2, 1, 1), xreg = GDP_tr[-length(GDP_tr)])

#Original Model aic = -600.48

arimax.gdp<-arima(Rt_GDP, order = c(2, 1, 1), xreg = Rt_INDPRO_quar)
tsdisplay(arimax.gdp$residuals)
tsdiag(arimax.gdp)
```

```{r}
# Unemployment
summary(arima(Rt_UNEPLOY,order=c(6,0,5),xreg=Rt_CPI))
summary(arima(Rt_UNEPLOY,order=c(6,0,5),xreg=Rt_INDPRO))
summary(arima(Rt_UNEPLOY,order = c(6, 0, 5), xreg = UNEMPLOY_tr[-length(CPI_tr)]))
summary(arima(Rt_UNEPLOY, order = c(6, 0, 5), xreg = UNEMPLOY_tr[-length(UNEMPLOY_tr)]))
summary(arima(Rt_UNEPLOY,order = c(6, 0, 5), xreg = UNEMPLOY_tr[-length(INDPRO_tr)]))

#Original ARIMA Model aic = -1160.93

arimax.une<-arima(x = Rt_UNEPLOY, order = c(6, 0, 5), xreg = Rt_INDPRO)
tsdisplay(arimax.une$residuals)
tsdiag(arimax.une)
```

```{r}
# Industrial Production
summary(arima(Rt_INDPRO, order = c(1, 0, 3), seasonal = list(order = c(1,0,0), period = 24), xreg=Rt_CPI))
summary(arima(Rt_INDPRO, order = c(1, 0, 3), seasonal = list(order = c(1,0,0), period = 24), xreg=Rt_UNEPLOY))
summary(arima(Rt_INDPRO, order = c(1, 0, 3), seasonal = list(order = c(1,0,0), period = 24), xreg=CPI_tr[-length(CPI_tr)]))
summary(arima(Rt_INDPRO, order = c(1, 0, 3), seasonal = list(order = c(1,0,0), period = 24), xreg=UNEMPLOY_tr[-length(UNEMPLOY_tr)]))
summary(arima(Rt_INDPRO, order = c(1, 0, 3), seasonal = list(order = c(1,0,0), period = 24), xreg=INDPRO_tr[-length(INDPRO_tr)]/10000))

#Original ARIMA Model aic = -1859.13

arimax.ip<-arima(Rt_INDPRO, order = c(1, 0, 3), seasonal = list(order = c(1,0,0), period = 24), xreg=INDPRO_tr[-length(INDPRO_tr)]/10000)
tsdisplay(arimax.ip$residuals)
tsdiag(arimax.ip)
```

## Prediction and Visualization
```{r}
fmodel.cpi<-arima(Rt_CPI, order = c(2, 0, 5), seasonal = list(order = c(1,0,1), period = 24))
fmodel.gdp<-arima(Rt_GDP, order = c(2, 1, 1), xreg = Rt_INDPRO_quar)
fmodel.une<-arima(x = Rt_UNEPLOY, order = c(6, 0, 5), xreg = Rt_INDPRO)
fmodel.ip<-arima(Rt_INDPRO, order = c(1, 0, 3), seasonal = list(order = c(1,0,0), period = 24), xreg=INDPRO_tr[-length(INDPRO_tr)]/10000)
```
```{r}
INDPRO_quar <- NULL
for(i in 1 : length(INDPRO))
{
  if(i %% 3 == 1)
  {
    INDPRO_quar <- rbind(INDPRO_quar, INDPRO[i])
  }
}
Rt_qINDPRO <- tail(diff(log(INDPRO_quar))[-1],5)

rt_ip <- tail(diff(log(INDPRO))[-1],16)
ip<-(tail(INDPRO,16))[-16]/10000

pr.cpi<-predict(fmodel.cpi,16)
pr.gdp<-predict(fmodel.gdp,newxreg=Rt_qINDPRO,5)
pr.une<-predict(fmodel.une,newxreg=rt_ip,16)
pr.ip<-predict(fmodel.ip,newxreg=ip,15)

par(mfrow=c(1,1))
plotr(CPIAUCNS,rt_cpi,pr.cpi,16,"CPI",c(-.0069,.0105))
plotr(GDP,rt_gdp,pr.gdp,5,"GDP",c(.0008,.022))
plotr(UNEMPLOY,rt_unemploy,pr.une,16,"Unemployment Level",c(-.065,.05))
plotr(INDPRO,rt_indpro,pr.ip,15,"Industrial Production",c(-.015,.015))
```

